---
title: "R function *treetag.fertilizer*"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

The R function *treetag.fertilizer* calls a local installation of *TreeTagger* (Schmid, 1994) and identifies sentences in the parsed corpus. The output is a dataframe with tokens in rows and annotations in columns.

## Usage

treetag.fertilizer(pathToTreetagger, pathToCorpus, language, sentence_delim = c("!", "?", ".", ":", ";"))

## Arguments  

 | 
 ---------|----------------------------------------------------------------------------------------------------
pathToTreeTagger | Character string specifying the path to the local installation of TreeTagger, e.g., "/home/user/TreeTagger/"
pathToCorpus | Character string specifying the path to the corpus files, e.g., "./data/"
language |	Character string naming the language of the corpus, e.g., "english" or "german"
sentence_delim |	Character vector with tokens specifying sentence delimiters

## Details  

Note that the function calls *TreeTagger* with default configuration and has no options to change that. The language argument specifies the language-specific tagging script that *TreeTagger* uses to parse the corpus. The language label should match the last part of the respective file name (e.g., *tree-tagger-german* for parsing German-language data). The function uses !?.:; as sentence delimiters by default. Enter a character vector with different elements to change sentence delimiters.

## Comparison to *treetag* in the *koRpus* package  

The function is similar to the function *treetag* in the *koRpus* package (Michalke, 2018), however, much faster. *TreeTagger* itself is very quick but sentence identification with *treetag* is slow and slows down with increasing corpus size. *treetag.fertilizer* speeds up sentence identification and is much less affected by corpus size (see Figure below) while using the most simplistic approach you have ever seen (see R code below).

```{r plot, echo=FALSE}

df<-readRDS("./data.Rda")

df<-df[-c(1:9, 11:19, 25:33, 35:43),]
fertil<-df[1:6,]
koRpus<-df[7:12,]

plot(koRpus$TIME ~ koRpus$SIZE, type = "b", col = "blue", ylab = "Time elapsed in seconds", xlab = "Corpus size in number of sentences")
lines(fertil$TIME ~ fertil$SIZE, type = "b", col = "green")
legend(5000, 200, legend=c("treetag{koRpus}", "treetag.fertilizer"),
       col=c("blue", "green"), lty=1, cex=1, pch = 1, box.lty=0)

```

## R code  

```{r, code = readLines("fcn_treetag-fertilizer.R")}
```

## References  

Michalke, M. (2018). koRpus: An R Package for Text Analysis. Available online at https://cran.r-project.org/web/packages/koRpus/index.html, February 22, 2020.<br>
Schmid, H. (1994). Probabilistic Part-of-Speech Tagging Using Decision Trees. In *Proceedings of International Conference on New Methods in Language Processing*. Manchester, England. Available online at http://www.cis.uni-muenchen.de/~schmid/tools/TreeTagger/, February 22, 2020. 

## Contributors  

Daniel Jach <danieljach\@protonmail.com<br>

## License and Copyright  


&copy; Daniel Jach, University of Zhengzhou, China

Licensed under the [MIT License](LICENSE).